\documentclass[10pt,twocolumn]{article}

\usepackage[margin=0.72in,columnsep=0.25in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{flushend}
\usepackage[protrusion=true,expansion=false]{microtype}
\usepackage{xurl}
\usepackage[hidelinks]{hyperref}

\setlist{nosep,leftmargin=*}
\setlength{\parindent}{1em}
\setlength{\parskip}{0pt}
\urlstyle{same}

\title{High-Resolution ConvNeXtV2 for Identity-Document Fraud Detection}
\author{Hanif Noer Rofiq\\
\small Kaggle: \texttt{hanifnoerr}}
\date{FREUID Challenge 2026\\July 14, 2026}

\begin{document}
\maketitle

\begin{abstract}
We describe our submission to the FREUID Challenge 2026, a binary
identity-document fraud detection benchmark. The system fine-tunes a
ConvNeXtV2-Large classifier at $672\!\times\!672$ resolution using all 69,352
labeled training images. The training recipe is intentionally direct: mild
photometric and geometric augmentation, binary cross-entropy, AdamW, cosine
learning-rate decay, and mixed-precision optimization. A single model obtained
a public leaderboard FREUID score of \textbf{0.00283} (lower is better) on the
complete 142,818-image submission. The
private score was unavailable when this report was prepared. We release the
training notebook, frozen checkpoint identity, and a network-isolated Docker
inference path.
\end{abstract}

\section{Introduction}
Identity-document fraud may involve digital editing, generated content,
physical manipulation, or recapture through print-and-scan and display-camera
pipelines. These processes can alter both semantic content and weak imaging
traces. FREUID evaluates a detector on genuine and fraudulent document images,
including document domains not represented in the visible training data
\cite{the-freuid-challenge-2026-ijcai-ecai}. For each image $x$, a method emits
a continuous fraud score $p(y=1\mid x)$; larger values denote stronger evidence
of fraud.

The challenge metric combines the area under the detection-error trade-off
curve (AuDET) with APCER at 1\% BPCER. The resulting FREUID score lies in
$[0,1]$ and is minimized. This operating regime rewards ranking quality while
also penalizing attacks that remain undetected at a low bona-fide error rate.

Our final system uses one high-resolution ConvNeXtV2-Large model. We selected
this design because convolutional feature hierarchies provide a useful balance
between global document structure and localized texture evidence, while the
$672$-pixel input retains more manipulation detail than the backbone's native
$384$-pixel fine-tuning resolution.

\section{Data}
We use only the official FREUID training set. It contains 69,352 RGB document
images with binary labels: 40,005 bona-fide samples and 29,347 attacks. The
visible data cover five country/document-type groups: Egypt, Guinea, Benin,
Mozambique, and Mauritius. We do not use external identity-document images,
pseudo-labels, or synthetic training samples.

During the initial public phase, 7,821 test images were available although the
sample submission contained 142,818 identifiers. Following the organizer's
protocol, the unavailable identifiers were assigned placeholders and were not
evaluated at that stage. After the complete test release, the selected final
submission was regenerated from 142,818 resolved images. It contains model
predictions for every identifier and no placeholders. The Docker pipeline uses
the same rule: it produces one prediction for each image mounted by the
organizer.

The only external model resource is the ConvNeXtV2-Large FCMAE checkpoint
distributed with \texttt{timm}. This initialization was learned with the FCMAE
procedure and subsequently fine-tuned on ImageNet classification data
\cite{woo2023convnextv2,wightman2019timm}.

\section{Method}
\subsection{Architecture}
ConvNeXtV2 augments the modern ConvNeXt design with Global Response
Normalization and is co-designed with fully convolutional masked autoencoding
\cite{woo2023convnextv2}. We instantiate the Large variant through
\texttt{timm}, replace its classification head with one output logit $z$, and
compute the submitted probability as $\sigma(z)$. No ensembling, auxiliary
classifier, metadata feature, threshold calibration, or test-time augmentation
is used.

\subsection{Image Processing}
For training, each RGB image undergoes a bicubic random resized crop to
$672\!\times\!672$ with area scale in $[0.88,1.0]$. Color jitter is applied with
probability 0.5 (brightness 0.14, contrast 0.14, saturation 0.05), Gaussian blur
with probability 0.12 (kernel 3, $\sigma\in[0.1,1.0]$), and rotation within
$\pm1.5^\circ$. We then apply ImageNet mean and standard-deviation
normalization.

At inference, the shorter image side is resized to 672 pixels with bicubic
interpolation, preserving aspect ratio, followed by a $672\!\times\!672$ center
crop and the same normalization. This deterministic transform is shared by the
Colab inference notebook and Docker entry point.

\section{Training}
The model was trained on one Google Colab G4 runtime exposing 96~GB of GPU
memory. The run used all labeled samples (\texttt{VAL\_TYPE=None}); therefore,
no held-out validation metric was used to select the reported checkpoint. This
choice maximized the labeled data available to the final public model but makes
the leaderboard the only reported generalization measurement.

\begin{table}[t]
\centering
\caption{Frozen training configuration.}
\label{tab:training}
\small
\begin{tabular}{@{}ll@{}}
\toprule
Setting & Value \\
\midrule
Input resolution & $672\times672$ \\
Epochs & 3 \\
Batch size & 24 \\
Optimizer & AdamW \\
Initial learning rate & $1\times10^{-5}$ \\
Weight decay & 0.05 \\
Loss & BCE with logits \\
Schedule & cosine, $T_{\max}=3$ \\
Gradient clipping & global norm 1.0 \\
Random seed & 42 \\
Data-loader workers & 12 \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:training} summarizes the frozen configuration. We optimize all
network parameters without class weighting. PyTorch automatic mixed precision
uses bfloat16 when supported and float16 otherwise; gradient scaling is enabled
for float16. Inputs and model parameters use channels-last memory format, and
TF32 is enabled for supported matrix and convolution operations. The optimizer
is AdamW with an initial learning rate of $10^{-5}$ and weight decay 0.05. A
cosine annealing schedule spans the three training epochs. Gradients are clipped
to a maximum global norm of 1.0.

Because the final run has no validation partition, the checkpoint named
\texttt{best.pt} is updated after every epoch. The selected artifact is the
epoch-3 checkpoint produced by the frozen notebook.

\section{Results}
The selected complete-test ConvNeXtV2 submission achieved a public leaderboard
FREUID score of \textbf{0.00283}. Lower scores are better. All 142,818 rows were
generated from resolved test images. The private score was unavailable when
this report was prepared, so we do not report or infer a private-set result.
The submission is produced by a single checkpoint and a single deterministic
center-crop inference pass.

\section{Reproducibility}
The Docker build retrieves the selected checkpoint from public storage and
verifies its SHA-256 before embedding it in the image. Runtime inference
requires no network access. Dependencies are pinned in
\path{reproducibility/requirements.txt}; the base image is
\texttt{pytorch/pytorch:2.4.1-cuda12.1-cudnn9-runtime}.

The organizer mounts a flat image directory at \path{/data}. The container
converts each supported image to RGB, applies the deterministic preprocessing,
runs sigmoid scoring, and writes exactly two columns, \texttt{id,label}, to
\path{/submissions/submission.csv}. The identifier is the input filename stem.
Predictions are checked for uniqueness, finiteness, and membership in $[0,1]$.

\begin{small}
\begin{verbatim}
cd reproducibility
docker build -t freuid-repro .
mkdir -p out
docker run --rm --gpus all \
  --network none \
  -v /path/to/images:/data:ro \
  -v "$PWD/out:/submissions" \
  freuid-repro
\end{verbatim}
\end{small}

The reference evaluation target is one NVIDIA A100 40~GB GPU with at most 24
CPU cores. The default Docker batch size is 16 and the worker count is 8; both
may be changed through environment variables without changing model outputs.

\section{Limitations}
The reported score comes from the public split only. The selected run trains on
all labels and consequently provides no independent estimate of calibration or
out-of-domain performance. It also uses one center crop, which may discard cues
near the long image boundary. These choices favor a simple and auditable final
pipeline but leave room for document-type holdouts, multi-crop evaluation, and
model ensembles in future work.

\section{Conclusion}
Our submission is a single high-resolution ConvNeXtV2-Large fraud classifier
trained on the complete official training set. A small augmentation policy and
standard binary optimization were sufficient to obtain a public FREUID score of
0.00283 on the complete test submission. The accompanying frozen checkpoint,
notebook, and network-isolated
Docker image specify the complete path from an input image directory to the
submission file.

\section{Artifact Manifest}
The public implementation is available on
\href{https://github.com/hanifnoerr/freuid-2026-reproducibility}{GitHub}. Model
and training code were frozen before the private test release. The identifiers
below define the exact reported system.

\begin{description}[style=nextline,font=\normalfont\bfseries]
\item[Code freeze]
\path{freuid-code-freeze-2026-07-13}\\
Commit \path{707309a0fb08b176858bfb4e9909b45ef728cdb5}

\item[Model identifier]
\path{convnextv2_large.fcmae_ft_in22k_in1k_384}

\item[Training notebook]
\path{notebooks/freuid_convnextv2_g4_672_alltrain_best_public.ipynb}\\
SHA-256:
\nolinkurl{eeeecd050a11e06bfd4ede9f930c4807564867c0c30ec7432029c5939e20fa57}

\item[Selected checkpoint]
Epoch 3, file \path{best.pt}, approximately 2.2~GB.\\
SHA-256:
\nolinkurl{bb3870c09ec7fa21255df1cff40b6cd2ff5a7290904562d8e43a284e4ba5c41a}

\item[Checkpoint storage]
\url{https://drive.google.com/drive/folders/15pj--qzgwVzq-KjH7kJUcxnTS3ZA5c2P}

\item[Reported submission]
\path{submission_convnextv2_epoch03_newest_a100.csv}\\
142,818 rows; SHA-256:\\
\nolinkurl{94a6ae437bf44848ef51490bdc90475d8454445f488b97cca124cf3a62d48b9b}

\item[Container contract]
Input: flat image directory at \path{/data}.\\
Output: \path{/submissions/submission.csv}.\\
Columns: \texttt{id,label}; one finite score per input image.
\end{description}

\begingroup
\raggedright
\bibliographystyle{ieeetr}
\bibliography{references}
\endgroup

\end{document}
